% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[utf8]{inputenc}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Stephen Pedrosa Eilert}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://github.com/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

\begin{flushright}

{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +11 55 85 962-1234 \\
    Fax: &  +11 55 85 962-5678 \\
    Email: & \href{mailto:spedrosa@gmail.com}{\tt spedrosa@gmail.com} \\
    Homepage: & \href{http://www.stat-or.unc.edu/}{\tt http://www.stat-or.unc.edu/} \\
  \end{tabular}
\end{minipage}
\end{flushright}
\section*{Experience Overview}

Stephen Eilert has a Degree in Computer Science. He is a professional computing
specialist with more than 5 years experience in advanced software analysis and design,
having gathered knowledge on various platforms and programming languages. Among these
are: C, C++, C\#, Java, Python and Ruby.
Stephen Eilert has a Degree in Computer Science.
He has advanced English language skills, having attained the Cambridge FSOL FCE
Certificate.


\section*{Education}

\begin{itemize}
  \item B.S. Computer Science, Universidade Federal do Ceará, 2008.
\end{itemize}

\section*{Main Skills}
\begin{itemize}
  \item Microsoft Technologies (.NET Framework, API Win32, SQL Server)
  \item Oracle Technologies (Java Platform including J2SE, J2EE and J2ME) and support
    technologies such as Hibernate, Spring, Struts.
    Oracle Database and Oracle Application Server.
  \item Unix (Linux, NetBSD, Solaris, OS-X)
  \item UML Modeling
  \item Programming Languages: Ruby, Python, Lua, C, C++, C\#, Java, Objective C, Scheme, Lisp
  \item Development methodologies such as RUP and agile such as SCRUM
  \item Tools: Rational Rose, Rational Unified Modeler, Enterprise Architect, Microsoft
Visual Studio, Eclipse, Ant, debuggers and profilers (language and platform
specific), unit tests and continuous integration (CruiseControl, Luntbuild),
\end{itemize}

\section*{Certifications}
\begin{itemize}
  \item Sun Certified Java Programmer - SCJP 5.0
  \item Cambridge FSOL FCE - University of Cambridge
\end{itemize}

\section*{Employment}

\begin{itemize}
\item DETRAN-CE (Department of Transportation, CE), 2010 - Current
\item Instituto Atlântico, 2004 - 2009
\item Media System, 2003 - 2004
\end{itemize}

\section*{Project Experience}
\begin{tabular}{| l | p{8cm} | l | l | l |}
  \hline
  \textbf{Duration} & \textbf{Objective} & \textbf{Customer} & \textbf{Customer Segment} & \textbf{Role} \\
  \hline
  6 months & Development of a completely new financial system using the Calypso platform, interfcing with existing mainframe systems. & HSBC & Financial & Analyst \\
  \hline
  5 months & Creation of a complete bettig platform front-end for a very large betting operator (in Ruby on Rails) & LVS & Software Development & Developer
  \hline
\end{tabular}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
